Download data

### 2024-03-01 scripts/subsetDataforCrews.Rmd
fn to wriite out rought flowering phenology

spp_needed <- read.csv('../data/raw/2024sos_species-FIXED.csv') %>% 
  unite('binomial', genus:species) %>% 
  select(binomial, contract)

@@

spp_needed <- rename(spp_needed, taxon = binomial)
p2ts <- '/media/steppe/hdd/SeedPhenology/data/processed/timestamps'
lapply(X = teams_list, 
       FUN = phen_tabulator,
       path = p2ts, 
       admu = admin_boundaries, 
       target_species = spp_needed
       )

>>>>

spp_needed <- read.csv('../data/raw/2024sos_species-FIXED.csv') %>% 
  unite('binomial', genus:species) %>% 
  select(binomial, contract) %>% 
  mutate(binomial = str_trim(binomial))

@@

spp_needed <- rename(spp_needed, taxon = binomial)

p2ts <- '/media/steppe/hdd/SeedPhenology/data/processed/timestamps'
lapply(
  X = teams_list, 
  FUN = phen_tabulator,
  path = p2ts, 
  admu = admin_boundaries, 
  target_species = spp_needed
  )
